Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

In the {\em find-all} version of the problem, the goal is to report, for each rectangle $r \in R$, the entire $\cross_H(r)$ sorted by y-coordinate. Formally, if $\cross_H(r) = \set{h_1, h_2, ..., h_z}$ (for some $z \ge 1$), we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.

@@

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$

>>>>

In the {\em find-all-sorted} version of the problem, the goal is to report, for each rectangle $r \in R$, the entire $\cross_H(r)$ sorted by y-coordinate. Formally, if $\cross_H(r) = \set{h_1, h_2, ..., h_z}$ (for some $z \ge 1$), we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.

@@

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$ --- where $\cross_H(r^*)$, defined in \eqref{eqn:cross}, is the set of segments in $H$ crossing $r^*$ --- which is an instance of the find-all-sorted version of Problem $\mathscr{D}$.
